Word learning at the semantics pragmatics interface

### 2020-04-17 paper/supplementary_material.Rmd
add figure

```{r fig1,echo = F, fig.align = "center", fig.cap = "Schematic experimental procedure with screenshots from the experiments.", out.width="100%"}
knitr::include_graphics("../graphs/method_overview.png")
```

>>>>

```{r fig1,echo = F, fig.align = "center", fig.cap = "Schematic experimental procedure with screenshots from the experiments.", out.width="100%"}
knitr::include_graphics("../figures/method_overview.png")
```
